---
title: "Transformation of truthtables into NAND-based DAG algorithms"
author: "David DORET"
date: "September 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Transformation of truthtables into NAND-based DAG algorithms

#' Transformation: truth tables to DAG
#'
#' I'll provide more details as soon as I have a moment to document this. \cr
#' But haricot has now a logically neutral transformation,
#' that takes an arbitrary truth table algorithm as input,
#' and transforms it into a DAG algorithm.
#'
#' @examples
#' # Create a random truth table algorithm with input dimension 8 and output dimension 8:
#' truthtable <- algo_tt$new(8,8)$do_randomize_outputs();
#' # Display the upper part of the truth table in the console:
#' cat(substr(truthtable$get_prettystring(),1,200));
#' # Transform the truth table to a DAG algorithm:
#' dag <- atomize(truthtable);
#' #

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
